An investigation into the contentious phylogenetic results of the *Mixta* species

### 2021-05-02 Manuscript/Manuscript_Paper.Rmd
Update Manuscript_Paper.Rmd

The four analyses conducted in this study agreed on a closest relative for only four of these genes – *atpA*, atpG*, *rpoB*, and *rpoC* – for both *M. calida* and *M. gaviniae*. This closest relative was *P. septica* for these genes. The other genes were more closely related to *P. agglomerans*, *E. tasmaniensis*, *E. amylovora*, and *E. cloacae* and these varied amongst the analyses. The gene *rpoD* was the only gene that was said to be closely related to *E. cloacae* by one of the analyses. The NTS genetic distance analysis labelled both the *Mixta* species as being closely related to *E. cloacae* and the remaining three analyses labelled this gene as being closely related to *P. septica*.

>>>>

The four analyses conducted in this study agreed on a closest relative for only four of these genes – *atpA*, *atpG*, *rpoB*, and *rpoC* – for both *M. calida* and *M. gaviniae* (Figures 10A and 10B). This closest relative was *P. septica* for these genes. The other genes were more closely related to *P. agglomerans*, *E. tasmaniensis*, *E. amylovora*, and *E. cloacae* and these varied amongst the analyses (Figures 10A and 10B). One only of the genes, *rpoD*, was said to be closely related to *E. cloacae* by one of the analyses; the NTS genetic distance analysis labelled both the *Mixta* species as being closely related to *E. cloacae* and the remaining three analyses labelled this gene as being closely related to *P. septica* (Figures 10A and 10B).

```{r Figure10, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Figure 10. The closest relatives to the *M. calida* (**A**) and *M. gaviniae (**B**) MLSA genes for each of the four analyses. The colour of the tiles represent the different species to which the gene is most closely related.", fig.width=6.5}
four_cal <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure10A_PhyloTreeFour_calida.csv", 
                     stringsAsFactors = FALSE) %>%
  pivot_longer(cols = Distance_NTS:Identity_AAS, names_to = "Analysis", values_to = "Species") %>%
  mutate(Gene = substring(Gene, first = 7),
         Analysis = factor(Analysis, levels = c("Distance_NTS", "Distance_AAS", "Identity_NTS", "Identity_AAS"), ordered = TRUE),
         Species = factor(Species, levels = Spp, ordered = TRUE))

four_gav <- read.csv("C:/Users/Kim/OneDrive/2020_3Fall/Biology_396/10_Tables_and_Figures/Figure10B_PhyloTreeFour_gaviniae.csv", 
                     stringsAsFactors = FALSE) %>%
  pivot_longer(cols = Distance_NTS:Identity_AAS, names_to = "Analysis", values_to = "Species") %>%
  mutate(Gene = substring(Gene, first = 7),
         Analysis = factor(Analysis, levels = c("Distance_NTS", "Distance_AAS", "Identity_NTS", "Identity_AAS"), ordered = TRUE),
         Species = factor(Species, levels = Spp, ordered = TRUE))

my_colours2 <- c("#A6CEE3", "#1F78B4",  # P. septica and P. agglomerans
                 "#B2DF8A", "#33A02C",  # E. tasmaniensis and E. amylovora
                 "#FDBF6F")             # E. cloacae

cal <- ggplot(four_cal, aes(x = Analysis, y = Gene, fill = Species)) +
  geom_tile() +
  scale_fill_manual(values = my_colours2,
                    labels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "E. cloacae")) +
  labs(fill = "Closest Relative") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(face = "italic"),
        legend.text = element_text(face = "italic"),
        text = element_text(size = 12,  family = "Times New Roman"))

gav <- ggplot(four_gav, aes(x = Analysis, y = Gene, fill = Species)) +
  geom_tile() +
  scale_fill_manual(values = my_colours2,
                    labels = c("P. septica", "P. agglomerans", "E. tasmaniensis", "E. amylovora", "E. cloacae")) +
  labs(fill = "Closest Relative") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        axis.text.y = element_text(face = "italic"),
        legend.text = element_text(face = "italic"),
        text = element_text(size = 12,  family = "Times New Roman"))

ggarrange(cal, gav, 
          labels = c("A", "B"),
          font.label = list(family = "Times New Roman"),
          common.legend = TRUE, 
          legend = "right")
```
